### 2022-05-22 CV2/papers.tex
-
work on cv
papers

\section{{Publications}}

@@

\section{{Preprints}}

@@

@@

\bigskip
\begin{center}
Last Updated on March 21, 2022
\end{center}

>>>>

\section{Publications}

@@

\section{Preprints}

@@

\item \textbf{The First Optimal Acceleration of High-Order Methods in Smooth Convex Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2205.09647}{\em \color{black}arXiv preprint (May 2022)}
\item \textbf{The First Optimal Algorithm for Smooth and Strongly-Convex-Strongly-Concave Minimax Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2205.05653}{\em \color{black}arXiv preprint (May 2022)}

@@
